### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction/strip.tex
minor changes

The following lemma is convenient to substitute equals by equals in a theorem.
Recall the equality (≡) is symmetric and transitive, and we use these properties
without any mention.

@@

The user of \Metis will probably note another rule in the derivations related
with these subgoals, the \negate rule. Since \Metis proves a conjecture by
refutation, to prove a subgoal, \Metis assumes its negation with the \negate
rule. This negation ocurrs always after the application of the \strip rule which
as we mentioned before it is the rule that introduces each subgoal.

>>>>

The following lemma is convenient to substitute in a theorem equals by equals in
the conclusion of the sequent. Recall the equality (≡) is symmetric and
transitive, and we use these properties without any mention.

@@

The user of \Metis will probably note another rule in the derivations related
with these subgoals, the \negate rule. Since \Metis proves a conjecture by
refutation, to prove a subgoal, \Metis assumes its negation using the \negate
rule. This rule always ocurrs in the \TSTP derivation after the application of
the \strip rule that introduces the subgoal.
